---
title: "Logistic Regression with Smarket Dataset"
output:
  html_document:
    df_print: paged
---

#### Prepare the package and data

```{r}
library(ISLR)
attach(Smarket)
```


```{r}
head(Smarket)
```


#### Split data into testing and training
```{r}
train <- Smarket[Year < 2005, ]
test <- Smarket[Year == 2005, ]
```

#### Train a model using Logistic Regression
In this tutorial, we will fit a logistic regression model in order to predict `Direction` using `Lag1` through `Lag3`.
Model = Direction ~ Lag1 + Lag2 + Lag3

The `glm()` function fits **generalized linear models**, a class of models that includes logistic regression. 

The syntax of the `glm()` function is similar to that of `lm()`, except that we must pass in the argument `family=binomial` in order to tell `R` to run a logistic regression rather than some other type of generalized linear model.

The basic syntax for `glm()` function in logistic regression is `glm(formula,data,family)`.

Following is the description of the parameters used:

* **formula** is the symbol presenting the relationship between the variables.
* **data** is the data set giving the values of these variables.
* **family** is R object to specify the details of the model. It's value is binomial for logistic regression.
```{r}
model <- glm(formula = Direction ~ Lag1 + Lag2 + Lag3, data = train, family = "binomial")
```

#### Evaluate model on the test set
```{r}
pred <- predict(model, test, type="response")
pred.logit <- rep("Down", length(pred))
pred.logit[pred >= 0.5] <- "Up"
```


See the classification result
```{r}
table(pred.logit, test$Direction)
```

```{r}
library(caret)
confusionMatrix(test$Direction, factor(pred.logit))
```

```{r}
library(pROC)
plot(roc(as.numeric(test$Direction),
         as.numeric(factor(pred.logit))))
```

#### References

* http://www.science.smith.edu/~jcrouser/SDS293/labs/lab4-r.html
* https://www.tutorialspoint.com/r/r_logistic_regression.htm