---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
attach(mtcars)
head(mtcars)
```
Suppose we start with part of the built-in mtcars dataset. In the examples below, we’ll use vs as the outcome variable, mpg as a continuous predictor, and am as a categorical (dichotomous) predictor.

```{r}
dt <- subset(mtcars, select = c(mpg, am, vs))
dt
```


In this example, mpg is the continuous predictor variable, and vs is the dichotomous outcome variable.

```{r}
fit <- glm(vs ~ mpg, data = mtcars, family = binomial(link = "logit"))
fit
```

```{r}
summary(fit)
```

Plotting

```{r}
library(ggplot2)
ggplot(dt, aes(x=mpg, y=vs)) + geom_point() + 
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)
```
```{r}
par(mar = c(4, 4, 1, 1)) # Reduce some of the margins so that the plot fits better
plot(dt$mpg, dt$vs)
curve(predict(fit, data.frame(mpg=x), type="response"), add=TRUE) 
```

Multiple Logistic Regression Model (two predictor variables)

```{r}
fit2 <- glm(vs ~ mpg + am, data = mtcars, family = binomial(link = "logit"))
fit2
```

```{r}
summary(fit2)
```

```{r}
library(predict3d)
ggPredict(fit2, se = TRUE, interactuve = TRUE, digits = 3)
```


### References

* https://cran.r-project.org/web/packages/ggiraphExtra/vignettes/ggPredict.html
* http://www.cookbook-r.com/Statistical_analysis/Logistic_regression/
* https://mgimond.github.io/Stats-in-R/Logistic.html